\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-01-28 manuscript/manuscript.tex
New Plots

\input{tables/rr_200}

\input{tables/rr_400}

\input{tables/rr_800}

From 
Table~\ref{table:rr_200}, 
the rejection rates are a little higher for $n = 200$, but they may still be 
drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
from Table~\ref{table:rr_400} that the rejection rate
is consistently above 50\%. For larger sample sizes, the rejection rate is 
consistently above 90\%. We can also
observe that the rejection rate is slightly higher for the $\gamma(8, 1)$ sample 
than for 
the $N(8, 8)$. As the strength of the temporal dependence increases, the 
rejection rate decreases, and the rejection
rate appears to be slightly higher for negative temporal dependence versus 
positive temporal dependence values of the same strength.

As shown in Tables~\ref{table:rr_800}, the rejection rates for this settings 
are very 
high (almost 1), indicating that under $H_A$, the test is very powerful 
(low probability of failed rejection $\beta$) when a large enough
sample size is used.

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/rr}
  \caption{A plot of the rejection rates as a function of $\tau$ for
 $n \in \{100, 200, 400, 800\}$ and marginal distribution 
 $\in \{N(8,8), \gamma(8,1)\}$.}
  \label{fig:rr}
\end{figure}

From 
Table~\ref{fig:rr}, 
the rejection rates are a little higher for $n = 200$, but they may still be 
drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
that the rejection rate
is consistently above 50\%. For larger sample sizes, the rejection rate is 
consistently above 90\%. We can also
observe that the rejection rate is slightly higher for the $\gamma(8, 1)$ sample 
than for 
the $N(8, 8)$. As the strength of the temporal dependence increases, the 
rejection rate decreases, and the rejection
rate appears to be slightly higher for negative temporal dependence versus 
positive temporal dependence values of the same strength.

The rejection rates for $n = 800$
are very 
high (almost 1), indicating that under $H_A$, the test is very powerful 
(low probability of failed rejection $\beta$) when a large enough
sample size is used.
